### 2011-01-10 docs/slides/result.tex
Batesian and Mullerian mimicry slides.
Slide updates before submission.

@@

	\begin{itemize}
	  \item \textbf{Objective}: Evaluate evolution of mimicry.
	  \item \textbf{Evaluation process}:
			\begin{itemize}
			  \item Calculate number mimicry rings.
			  \item Calculate size of mimicry rings:
					\begin{itemize}
					  \item Population of \textit{palatable} species.
					  \item Population of \textit{unpalatable} species.
					\end{itemize}			  
			\end{itemize}
		\item \textbf{Report parameters}:
			\begin{table}
			\centering
			\begin{scriptsize}
			\begin{spacing}{1.5}
			\begin{tabular}{| l | c |}
				\hline
					\textbf{Parameter} & \textbf{Value} \\ \hline
					Mimicry Ring hamming distance & 10 \% of the Pattern Size \\ \hline
					Number of Rings to report & 8 \\
				\hline
			\end{tabular}
			\end{spacing}
			\end{scriptsize}
			\caption{Parameters to mimicry ring report.}
			\label{tab:ring-report-control-parameters}
			\end{table}		
	\end{itemize}
}

@@

	\begin{itemize}
		\item \textbf{New experiment:} reduce predator memory to 1.\\
		\item \textbf{Observation:} The phenomenon of single large ring do not occur. 
		\item \textbf{Conclusion:} Similar to Franks and Noble.\\
		Multiple Mullerian mimics do not converge into one large ring.
	\end{itemize}	
}

>>>>

\frame
{
	\begin{center}
		\LARGE The Results
	\end{center}
}

@@

	\begin{itemize}
	  \item \textbf{Objective}: Evaluate evolution of mimicry.
	  \item \textbf{Evaluation process}:
			\begin{itemize}
			  \item Calculate number of mimicry rings.
			  \item Calculate size of mimicry rings:
					\begin{itemize}
					  \item Population of \textit{palatable} species.
					  \item Population of \textit{unpalatable} species.
					\end{itemize}			  
			\end{itemize}
		\item \textbf{Report parameters}:
			\begin{table}
			\centering
			\begin{scriptsize}
			\begin{spacing}{1.5}
			\begin{tabular}{| l | c |}
				\hline
					\textbf{Parameter} & \textbf{Value} \\ \hline
					Mimicry Ring hamming distance & 10 \% of the Pattern Size \\ \hline
					Number of Rings to report & 8 \\
				\hline
			\end{tabular}
			\end{spacing}
			\end{scriptsize}
			\caption{Parameters to mimicry ring report.}
			\label{tab:ring-report-control-parameters}
			\end{table}		
	\end{itemize}
}

@@

	\textbf{New experiment:}
	\begin{itemize}
		\item Reduce predator memory to 1.\\
		\item \textbf{Observation:} Single large ring do not occur. 
		\item \textbf{Conclusion:} Similar to Franks and Noble.\\
	\end{itemize}	
	Multiple Mullerian mimics do not converge into one large ring.
